On the performance of the MAC model

### 2018-11-14 2018_nips_vigil/appendix.tex
Added row references to full table in App. B.

\begin{table}[!h]
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
		\cmidrule{7-8} 
		&                        &  &               &     &                                & CoGenT-A    &  96.22   \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   & 96.27  \\

		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    93.28       \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    94.44       \\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B & 79.54          \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    95.62       \\
		\midrule
		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29           \\
		\cmidrule{7-8} 
		&                        &  &               &     &                                & CoGenT-A    &  95.47   \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\

		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    92.31       \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    92.95       \\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91          \\
		\cmidrule{7-8} 
		&                             &                                         &     &          &                & CogenT-B & 78.71          \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24         \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    94.55       \\
		\bottomrule
	\end{tabular}
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
	\label{tab:results_full}
\end{table}

@@

\begin{table}[!h]
	\centering
	\begin{tabular}{cCcCcCc}
		\toprule
		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}\cmidrule{7-8} 
		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\

>>>>

\begin{table}[!h]
	\centering
	\begin{tabular}{ccccCcCcc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17    & (a)      \\
		\cmidrule{7-8} 
		&                        &  &               &     &                                & CoGenT-A    &  96.22 &  \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   & 96.27 & \\

		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{98.06}          & CoGenT-A &  94.60	   &      \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    93.28   &    \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{98.16}          & CoGenT-A &  93.02    &     \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    94.44   &    \\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{5}{*}{CoGenT-A} & \multirow{5}{*}{30:52}     & \multirow{5}{*}{97.02}   &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}    & CoGenT-A & 96.88    &     \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B & 79.54     &    \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.91}          & CoGenT-A &  92.06     &    \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    95.62   &    \\
		\midrule
		\multirow{15}{*}{S-MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{28:30}  & \multirow{10}{*}{95.82} & \multirow{3}{*}{--}   & \multirow{3}{*}{--}  & CLEVR    & 95.29     & (b)      \\
		\cmidrule{7-8} 
		&                        &  &               &     &                                & CoGenT-A    &  95.47 & (d)  \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   &  95.58 & (e) \\

		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-A}         &       \multirow{2}{*}{97.48}          & CoGenT-A &  93.44      &   \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    92.31   &    \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11     & (i)    \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    92.95  & (j)     \\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{5}{*}{CoGenT-A}   & \multirow{5}{*}{28:33}   & \multirow{5}{*}{96.09}  &  \multirow{2}{*}{--}  &  \multirow{2}{*}{--}   & CoGenT-A & 95.91    & (c)      \\
		\cmidrule{7-8} 
		&                             &                                         &     &          &                & CogenT-B & 78.71       & (f)   \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24   & (g)      \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    94.55   & (h)    \\
		\bottomrule
	\end{tabular}
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models.}
	\label{tab:results_full}
\end{table}

@@

\begin{table}[!h]
	\centering
	\begin{tabular}{cCcCcCc}
		\toprule
		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\
